Prospective testing for the prevalence or transience of a shock effect over a set time horizon before it occurs

### 2022-07-31 prevalence_testing/postshocktest2022draft.tex
changes to unemployment example

The pandemic-induced recession of 2020 coincided with a one-month drop in US nonfarm payrolls in excess of 20 million people, or $13.57\%$, between March and April 2020.  This decline exceeds all other monthly declines by orders of magnitude, and hence then distance-based weighting employed in \citep{lin2021minimizing} could not reasonably hope to recover the full shock effect.  However, the test developed herein does not rely as heavily upon the assumption of a common shock distribution for donors or the assumption that the donors represent a rich and diverse sampling from that distribution.  What is potentially as important or more important is that the donor pool serve as an information source about the persistence of a shock effect in the time series under study, an information source based on the covariates that are posited to underlie the post-shock model dynamics.  It is therefore the latter that may best explain the performance of the decision-making method developed here.

>>>>

The pandemic-induced recession of 2020 coincided with a one-month drop in US nonfarm payrolls in excess of 20 million people, or $13.57\%$, between March and April 2020.  This decline exceeds all other monthly declines by orders of magnitude.  The distance-based weighting  in \citep{lin2021minimizing}, employing a convex combination of donor shocks, is known to be unable to extrapolate and thus recover the full shock effect.  However, the procedure developed herein does not rely as heavily upon the full or partial recovery of the shock effect.  What is potentially as important or more important is that the donor pool serve as an information source about the persistence of a shock effect in the time series under study, an information source based on the covariates that are posited to underlie the post-shock model dynamics.  It is therefore the latter that may best explain the performance of the decision-making method developed here.
